Datasheet for Climate Change Dataset

### 2024-12-15 other/datasheet/datasheet_template.qmd
update datasheet

---
title: "Datasheet for Climate Change Perspectives Dataset"
author: 
  - Lexi knight
thanks: "Code and data are available at: [https://github.com/LexiKnight/toronto_climate/tree/main](https://github.com/LexiKnight/toronto_climate/tree/main)."
date: today
date-format: long
abstract: "This datasheet presents the results of a study examining the relationship between age and education and individuals' likelihood to adopt climate-friendly behaviors. The data reveals patterns showing that younger people and those with higher levels of education are more inclined to engage in actions like reducing car usage and conserving energy. In contrast, older individuals are more likely to focus on long-term sustainability efforts such as energy efficiency. Financial barriers and skepticism about individual impact remain significant obstacles to broader climate action. The findings highlight the need for targeted interventions to make sustainable behaviors more accessible across demographic groups."
format: pdf
---

@@

2. **How many instances are there in total (of each type, if appropriate)?**
    - The dataset contains 500 instances, each corresponding to a single participant’s responses.

@@

6. **Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.**
    - There is some missing data for specific questions related to income, as some respondents chose not to provide this information.

@@

8. **Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.**
    - The dataset is split into 80% training and 20% testing for machine learning tasks.

9. **Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.**
    - There may be minor errors in the self-reported data, such as inconsistent responses or missing values.

@@

13. **Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these sub-populations are identified and provide a description of their respective distributions within the dataset.**
    - Yes, the dataset identifies sub-populations by age, education level, and income group, with the following distributions: 30% aged 18-35, 40% aged 36-50, and 30% aged 51-65; education levels range from high school to postgraduate education.

@@

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
    - The data was collected using an online survey platform. The survey was designed using Qualtrics and distributed via email and social media channels. The platform ensures that responses are stored securely and collected without bias.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
    - The dataset used a probabilistic sampling strategy with an oversampling of higher-education respondents to better capture differences in behavior based on education level.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
    - The data collection was managed by the researcher, with assistance from a small group of volunteers from local environmental organizations. No monetary compensation was provided.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
    - Data was collected over a 2-month period, from May to June 2024. The data accurately reflects participants' attitudes and behaviors regarding climate action at that time.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - Yes, the research was reviewed and approved by the University of Toronto’s Research Ethics Board (REB). Ethical approval documentation is available upon request.

@@

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - Yes, a data protection impact analysis was conducted. The analysis concluded that the data collection process adequately protected participants' privacy while enabling meaningful research outcomes.

12. *Any other comments?*
    - The ethical guidelines of the study ensured that the research process was transparent and respectful of participant privacy.

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
    - The data was cleaned to remove duplicate entries and handle missing values for certain demographic questions. Missing values for income were imputed based on similar demographic profiles.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
    - Yes, the raw data has been saved in a separate file and can be accessed upon request.

@@

4. *Any other comments?*
    - The data cleaning process aimed to ensure that the dataset was as accurate and representative as possible, while maintaining participant confidentiality.

@@

4. *Is there anything about the composition of the dataset or the way it was collected...*
    - The dataset offers a rich resource for studying the intersection of demographics and climate behavior, with potential for comparative studies in other urban areas.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- N/A
6. *Any other comments?*
	- N/A

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset may be distributed to third parties for academic research, policy analysis, or public service projects related to climate change behavior or urban studies. Distribution will be carefully managed to maintain privacy and confidentiality.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset will be distributed via GitHub and is accessible to anyone with the link. It will not have a DOI at this time, but plans for future DOI assignment are being considered for formal publication.
3. *When will the dataset be distributed?*
	- The dataset is available for distribution immediately. However, it may be updated periodically as new data becomes available or improvements are made.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset will be distributed under a Creative Commons Attribution-ShareAlike license (CC BY-SA), which allows for modification, distribution, and sharing of the dataset with proper attribution. No fees are associated with the use of this dataset. Licensing terms are available on the GitHub repository
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No third-party restrictions have been imposed on the dataset, but users are reminded to respect confidentiality and ethical guidelines regarding sensitive demographic data.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply to this dataset at the moment.
7. *Any other comments?*
	- The dataset is being made available to encourage academic, governmental, and non-governmental use, and contributors are encouraged to respect privacy and data security standards when using or sharing the dataset.

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset will be hosted on GitHub and maintained by the project team, which includes data scientists and urban studies researchers.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The dataset owner can be contacted via email at lexiknight@example.com for inquiries related to the dataset.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no erratum currently. If errors are identified, they will be documented and corrected in subsequent versions of the dataset.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset will be updated annually to reflect new data or to correct any errors. Updates will be communicated via GitHub, with a changelog provided for transparency.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset will adhere to the privacy policy outlined in the informed consent process, with all data retention guidelines strictly followed. Data will be retained for a maximum of five years, after which it will be deleted unless otherwise required by law or for ongoing research purposes.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset will be archived for historical reference. Users will be notified via GitHub whenever a new version is released, with clear indication of any major changes or updates.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Others are welcome to extend or augment the dataset through contributions via GitHub, following the guidelines provided. Contributions will be reviewed by the dataset maintainers for accuracy and relevance before being merged into the main repository.
8. *Any other comments?*
	- The maintenance of this dataset is a collaborative process, and the project team welcomes feedback and contributions from the broader community to ensure its continued growth and accuracy.

>>>>

---
title: "Datasheet for Climate Change Dataset"
author: 
  - Lexi knight
thanks: "Code and data are available at: [https://github.com/LexiKnight/toronto_climate/tree/main](https://github.com/LexiKnight/toronto_climate/tree/main)."
date: today
date-format: long
abstract: "This datasheet presents the results of a study examining the relationship between age and education and individuals' likelihood to adopt climate-friendly behaviors. The data reveals patterns showing that younger people and those with higher levels of education are more inclined to engage in actions like reducing car usage and conserving energy. In contrast, older individuals are more likely to focus on long-term sustainability efforts such as energy efficiency. Financial barriers and skepticism about individual impact remain significant obstacles to broader climate action. The findings highlight the need for targeted interventions to make sustainable behaviors more accessible across demographic groups."
format: pdf
---

@@

2. **How many instances are there in total (of each type, if appropriate)?**
    - The 2018 dataset contains 404 instances whereas the 2021 dataset contains 1400 instances, each corresponding to a single participant’s responses.

@@

6. **Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.**
    - There is some missing data for specific questions related to education, as some respondents chose not to provide this information.

@@

8. **Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.**
    - It not known based on the dataset itsef howevery we split the data into 80% training and 20% testing for machine learning tasks (to generate the models).

9. **Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.**
    - There are minor errors in the self-reported data, such as inconsistent responses. There is also instances where individuals did not respond such as stating their education level.

@@

13. **Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these sub-populations are identified and provide a description of their respective distributions within the dataset.**
    - Yes, the dataset identifies sub-populations by age and education level. Age is split into 18-35, 36-50, 51-65 and 65+. Education levels range from high school to postgraduate education however the specific categories vary between the 2018 and 2021 survey.

@@

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
    - The 2018 survey data was collected through online interviews that lasted approximately ten minues. Quotas were set by region, age and gender ensuring sampling only those 18 years and older. The 2021 survey data was collected online and over the phone.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
    - N/A

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
    - The data collection was managed by the researcher, the specifics are unknown.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
    - The 2018 survey data was collected between October 11 and October 18, 2018. The 2021 survey data does not specify the timeframe of collection.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - No, there is no mention of ethical review.

@@

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - No, there is no mention of conduction of a data protection impact analysis.

12. *Any other comments?*
    - N/A

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
    - The data was cleaned to keep missing values and rename variables more meaningful descriptions.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
    - Yes, the raw data has been saved in a separate file and can be accessed in the download script.

@@

4. *Any other comments?*
    - N/A

@@

4. *Is there anything about the composition of the dataset or the way it was collected...*
    - The dataset offers a rich resource for studying the intersection of demographics and climate behavior, with potential for comparative studies in other urban areas.

5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- N/A

6. *Any other comments?*
	- N/A

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- No, the dataset will not be distributed to third parties unless requested for academic research, policy analysis, or public service projects related to climate change behavior. The dataset is however accessibly via GitHub.

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset would be distributed via GitHub and is accessible to anyone with the link.

3. *When will the dataset be distributed?*
	- The dataset is available for distribution immediately.

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No, the dataset will not be distributed under a copyright or other IP license nor others similar.

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No third-party restrictions have been imposed on the dataset, but users are reminded to respect confidentiality and ethical guidelines regarding sensitive demographic data.

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply to this dataset at the moment.

7. *Any other comments?*
	- The dataset is being made available to encourage academic, governmental, and non-governmental use, and contributors are encouraged to respect privacy and data security standards when using or sharing the dataset.

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset will be hosted on GitHub and maintained by the Open Data Toronto project team, which includes data scientists and urban studies researchers.

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The dataset owner can be contacted at Opendatatoronto.ca
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no erratum currently. If errors are identified, they will be documented and corrected in subsequent versions of the dataset.

4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset will be updated annually to reflect new data or to correct any errors. Updates will be communicated via Open Data Toronto.

5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset will adhere to the privacy policy outlined in the informed consent process, with all data retention guidelines strictly followed. Data will be retained for a maximum of five years, after which it will be deleted unless otherwise required by law or for ongoing research purposes.

6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset will be archived for historical reference. Users will be notified via GitHub whenever a new version is released, with clear indication of any major changes or updates.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Others are welcome to extend or augment the dataset through contributions via GitHub, following the guidelines provided. Contributions will be reviewed by the dataset maintainers for accuracy and relevance before being merged into the main repository.

8. *Any other comments?*
	- N/A
